---
title: "Homework for Week_09"
author: "Lipi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions for LAB

- Use any dataset you would like and make two useful functions. 
- One that is a plot and one that is not. 
- Turn in your functions using RMarkdown with at least 2 examples for each function showing its flexibility. 
- Due, as always, at 1pm on Tuesday.


## Load the libraries
```{r}
library(tidyverse)
library(here)
library(tidyr)
library(dplyr)
library(ggplot2)
library(ggthemes)

library(gcookbook) # For the data set
```

## Read in the data
```{r}
## dataset 1 (heightweight)
# Already loaded with library
View(heightweight) 

## dataset 2 (heightweight_2)
url <- "https://raw.githubusercontent.com/rmcelreath/rethinking/master/data/Howell1.csv"
HW_2 <- read.csv(url, sep = ";")
str(HW_2)
View(HW_2)
```

## Let's create a function to convert height from cm to inches and weight from kgs to pounds
```{r}
## 1
# creates a function to convert height from cm to inches
cm_to_In <- function(cm) {
  In <- (cm / 2.54)
  return(In)
}

cm_to_In(154) # example to test

# convert height in HW_2 dataset from cm to inches
modified_HW_2 <-HW_2 %>% # gives new name and opens HW_2 dataset
  mutate(heightIn=(cm_to_In(height))) # mutates height from cm to inches using the function that we just created
head(modified_HW_2)



############################################################################################
## 2
# creates a function to convert weight from kg to pounds
kg_to_Lb <- function(kg) {
  Lb <- (kg * 2.205)
  return(Lb)
}

kg_to_Lb(95) # example to test

# convert weight in HW_2 dataset from kg to pounds
modifieddd_HW_2 <-HW_2 %>% # gives new name and opens HW_2 dataset
  mutate(weightLb=(kg_to_Lb(weight))) # mutates height from cm to inches using the function that we just created
head(modifieddd_HW_2)


############################################################################################
### Convert sex- binary to character-- DOUBT

sex_HW_2 <- modifieddd_HW_2 %>% # opens the dataset
  mutate(sex = recode(male, # choose column male and recode as required
                    "0" = "f", # 0 to f and 1 to m
                    "1" = "m")) %>% 
  mutate(x = as.character(levels(male))[sex]) # mutate male to sex and keep male as it is
View(sex_HW_2)

```

## Now let's create another function using a plot
This function will make it easier for us to create a histogram using a dataset that compares a variable by sex.
```{r}
plot_fun<-function(data, x, sex){ 
          ggplot(data, aes(x = {{x}},
                            fill = {{sex}}))+
    geom_histogram() + # creates a histogram
          # geom_dotplot(binaxis="y", stackdir = "up")+ # Creates a dot plot
          theme_classic()  + # sets classic theme
          theme(plot.title = element_text(hjust = 0.5), # Center alignment for title
                plot.background = element_rect(fill = "grey")) # Change background color
}

## Example 1 using heighweight data- height and sex
plot_fun(data = heightweight, x = heightIn, sex = sex) + # uses function to plot
  labs(x = "Height (In)", # Labels x and y axes
     title = "Comparison of the height of males and females") # adds label to title

# Save your plot 1
ggsave(here("Week_09","Output","Homework_ plot_1.png"),
       width = 7, height = 5) # in inches)


## Example 2 using sex_HW_2 data - weight and sex
plot_fun(data = sex_HW_2, x = weightLb, sex = sex) + # uses function to plot
  labs(x = "Weight (Lbs)", # Labels x and y axes
     title = "Comparison of the weight of males and females") # adds label to title

# Save your plot 2
ggsave(here("Week_09","Output","Homework_plot_2.png"),
       width = 7, height = 5) # in inches)
```

