---
title: "Homework for Week 09"
author: "Lipi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions for LAB

- Use any dataset you would like and make two useful functions. 
- One that is a plot and one that is not. 
- Turn in your functions using RMarkdown with at least 2 examples for each function showing its flexibility. 
- Due, as always, at 1pm on Tuesday.


Load the libraries
```{r}
library(tidyverse)
library(here)
library(tidyr)
library(dplyr)
library(tidytuesdayR)
library(ggplot2)
library(ggthemes)
```

Read in the data

```{r}
tdf_winners <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-07/tdf_winners.csv')
glimpse(tdf_winners)
View(tdf_winners)

```


```{r}
artwork <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-12/artwork.csv')
glimpse(artwork)
View(artwork)
```


```{r}
student_debt <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-09/student_debt.csv')
glimpse(student_debt)
View(student_debt)
```

# First Function

**Let's create a function to convert dollars (D) to rupees (R).**

State two examples: 

- 5 dollars to rupees
- 450 dollars to rupees

```{r}
unit_mm_to_m <- function(unit_mm) {
  unit_m <- (unit_mm / 1000)
  return(unit_m)
  }
unit_mm_to_m(1)
unit_mm_to_m(1000)
```

# Second Function

First let's create a simple ggplot

```{r}
student_debt %>%
  ggplot(mapping = aes(x = year, y = loan_debt, color = race)) + # assigning x and y axes
  geom_line() + # choose a type of geom
  geom_point() + # adding a geom layer for better visualization
  labs(x = "Year", y = "Loan Debt (in dollars, $)", 
       title = "The variation in debt of loan from students of different races") + # adds labels to axes
  theme(plot.title = element_text(hjust = 1.0)) + # centers plot title
  theme(panel.background = element_rect(fill = 'lightblue', color = 'purple')) +
  scale_x_continuous(breaks = c(1980, 1985, 1990, 1995, 2000, 2005, 2010, 2016, 2020)) + # set marks for x and y axes
  scale_y_continuous(breaks = c(2000, 4000, 6000, 8000, 10000, 12000, 14000, 16000)) +
  theme_igray()
```

Let's create a simple plot

```{r}
tdf_winners %>%
  drop_na(height, distance) %>%
  ggplot(mapping = aes(x = height, y = distance)) + # assigning x and y axes
  geom_line() # choose a type of geom
```

```{r}
artwork %>%
  drop_na(year, height) %>%
  ggplot(mapping = aes(x = year, y = height)) + # assigning x and y axes
  geom_line()
```

```{r}
library(gcookbook) # For the data set
# View(heightweight)
ggplot(heightweight, aes(x=weightLb, y=heightIn, fill = sex)) +
geom_dotplot(binaxis="y", stackdir = "up")
```

```{r}

url <- "https://raw.githubusercontent.com/rmcelreath/rethinking/master/data/Howell1.csv"
heightweight_2 <- read.csv(url, sep = ";")
str(heightweight_2)
View(heightweight_2)
```

```{r}
ggplot(heightweight_2, aes(x=weight, y=height)) +
geom_dotplot(binaxis="y")
```

