---
title: "Homework for Week 12 (iterative coding)"
author: "Lipi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# What do we have to do for today's lab?

You have a set of 4 .csv files in data/homework. Each of these files is a timeseries of temperature and light data collected in tide pools in **Oregon by Jenn Fields**. 

- Bring in all 4 files
- Calculate the mean and standard deviation of both temperature (Temp.C) and light (Intensity.lux) for each tide pool 
- Use both a for loop and map() functions in your script. (Basically, do it twice). 


### Load the libraries
```{r}
library(tidyverse)
library(here)
library(purrr)
```

## Bringing files using for loop function

### Bring in files from data folder
```{r}
# list files in the directory
HomePath <- here("Week_12", "Data", "homework") # point to the location on the computer in the data folder
TP_data <- dir(path = HomePath, pattern = ".csv") # looks for everything that has a .csv in the file name and is in the homework folder within the data folder

TP_data
```

### pre-allocate space for the loop
```{r}
# make an empty dataframe that has one row for each file and 5 columns
home_data <- data.frame(matrix(nrow = length(TP_data), ncol = 5))

# give the data.frame column names
colnames(home_data) <- c("filename","mean_temp", "mean_int", "sd_temp", "sd_int")
home_data
```

### Calculate mean and standard deviation

```{r}
for (i in 1:length(TP_data)){ # loops over 1:4 the number of files
  raw_TPdata <- read_csv(paste0(here(HomePath, TP_data[i]))) # reads in data
glimpse(raw_TPdata)

home_data$filename[i] <- TP_data[i] # First, add in the file name for each row in the filename column

home_data$mean_temp[i]<-mean(raw_TPdata$Temp.C, na.rm = TRUE) # calculate mean temp
home_data$mean_int[i]<-mean(raw_TPdata$Intensity.lux, na.rm = TRUE) # calculate mean int

home_data$sd_temp[i]<-mean(raw_TPdata$Temp.C, na.rm = TRUE) # calculate std dev of temp
home_data$sd_int[i]<-mean(raw_TPdata$Intensity.lux, na.rm = TRUE) # calculate std dev of int
}  

home_data # opens the data
```


## Bringing files using map function

### Bring in files from data folder
```{r}
# list the files in the directory
HomePath<-here("Week_12", "Data", "homework") # point to the location on the computer in the data folder
TP_purrr <- dir(path = HomePath, pattern = ".csv", full.names = TRUE) # looks for everything that has a .csv in the file name and is in the homework folder within the data folder (remember to use full names to make it work!)

TP_purrr # opens the data
```

### Read in the files while retaining the filename as a column and calculate mean and standard deviation in temperature and light intensity
```{r}
Home_purrr<-TP_purrr %>% # create new df, Home_purrr
  set_names() %>% # set's the id of each list to the file name
  map_df(read_csv, .id = "filename") %>% # map everything to a dataframe and put the id in a column called filename
  group_by(filename) %>% # grouped by file name
  summarise(mean_temp = mean(Temp.C, na.rm = TRUE), # summarized mean temp
            mean_int = mean(Intensity.lux, na.rm = TRUE), # summarized mean int
            sd_temp = sd(Temp.C, na.rm = TRUE), # summarized std dev of temp
            sd_int = sd(Intensity.lux, na.rm = TRUE)) # summarized std dev of int
Home_purrr # opens the data
```

