---
title: "Homework for Week_11"
author: "Lipi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = TRUE,
	warning = FALSE
)
```

# What are we supposed to do for today's lab?

Working with intertidal data. Today you will need to use skills that you have learned in **working with words** to clean up some issues with the character data and use what you learned today to **reorder your factors into orders that make sense**. (Also the **column headers could be better**...). HINT: New package idea to fix this is using the *janitor package*.

**Your goal, as per usual, is to make a plot, any plot where one of the axes is a factor. Save everything in the appropriate folders.**

You have two possible files to play with in the data folder (you don't HAVE to use both): intertidal.csv and intertidal_latitude.csv (as well as a data dictionary)

Importantly, if you decide to visualize anything by tide height it should go from **low to mid to high tide.**


# Load the libraries
```{r}
library(tidyverse)
library(here)
library(janitor)
library(tidyr)
library(dplyr)
library(ggplot2)
library(ggthemes)
```

# Read in the data
```{r}
intertidal<-read_csv(here("Week_11","Data","intertidaldata.csv"))

glimpse(intertidal)
View(intertidal)
```

# Now lets clean by using our knowledge from **working with words** lecture and **reordering factor** using knowledge from today's lecture
```{r}
clean_intertidal <- intertidal %>% 
  clean_names() %>% # renames the column titles in default case, snake_case (Janitor package)
  mutate(quadrat = str_replace_all(quadrat, pattern = "\\.|[0-9]", replacement = " ")) %>% # deletes unwanted numbers in quadrat column
  mutate(quadrat = str_trim(quadrat)) %>% # trims the white space from quadrat column
  mutate(quadrat = factor(quadrat, levels = c("Low","Mid","High"))) %>% # converts quadrat into factors and arranges them from low-> mid -> high, which makes sense!
  filter(site == "Dana Point") %>% # filters values for only one site, Dana Point
  drop_na() # filters out everything that is not a complete row
head(clean_intertidal)

```

# Let's make a simple plot
```{r Algae at Dana point, fig.align='center'}
clean_intertidal %>% # using the cleaned intertidal dataset
  ggplot(aes(x = quadrat, y = algae,
             fill = quadrat)) + # assigns xand y axes 
  geom_col() + # chooses the geom to make a plot
  labs(x = "Tidal Quadrats", y = "Algal count", 
       title = "Algal samples collected from different tidal quadrats at Dana Point") + # adds label to axes
  theme_minimal() + # chooses minimal theme to display
  theme(plot.title = element_text(hjust = 0.5), # center alignment for title
                plot.background = element_rect(fill = "beige")) # hanges background color
```

# Save your plot
```{r}
ggsave(here("Week_11","Output","Homework_for_Week_11.png"),
       width = 8, height = 4) # in inches)
```

