---
title: "Biogeochemical Data Script"
author: "Lipi"
date: "`r Sys.Date()`"
output: 
  html_document: 
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

# Introduction
Today we are going to work with **Biochemistry Data** to practice _RMarkdown_.


# Load the libraries
```{r}
library(here)
library(tidyverse)
library(ggthemes)
library(ggplot2)
library(kableExtra)
```

# Load the data
```{r}
ChemData<-read_csv(here("Week_06","Data", "chemicaldata_maunalua.csv"))
View(ChemData)
glimpse(ChemData)
```


# Remove all the NAs from your data to get a clean data
```{r}
ChemData_clean<-ChemData %>%
  drop_na() #filters out everything that is not a complete row
View(ChemData_clean)
```

# Make a table using the clean data
We will make a table for Spring Season with one sample from each Zone and note the following variables:

- Salinity
- Temperature
- pH

| **Zone**  | **Salinity** | **Temperature**  | **pH** |
|:----------|:------------:|:----------------:|:------:|
| Transition | 27.74029 | 23.75506 | 7.909 |
| Diffuse  | 29.12293 | 23.26102 | 8.005 |
| Ambient  | 34.57789 | 24.10860  | 8.088 |
| Offshore  | 34.60953 | 24.43115 | 7.975 |

```{r}
ChemData_clean %>%
  group_by(Zone) %>%
  summarise(MeanSalinity = mean(Salinity, na.rm = TRUE),
            MeanTemperature = mean(Temp_in, na.rm = TRUE),
            MeanpH = mean(pH, na.rm = TRUE)) %>%
  kbl() %>% # make it a kable table
  kable_classic()

```



# Make a simple ggplot
```{r , fig.asp=1.25, fig.height=5, fig.width=8, fig.align='center', fig.cap="This is a histogram of pH values from different zones", echo =  FALSE}
ChemData_clean %>%
  ggplot(aes(y = pH, fill = Zone))+ # assign x and y axes
  geom_histogram() +
labs(x = "Count", y = "pH value", title = "Variation in pH values of the samples collected from four different zones") +
theme_classic() +
theme(axis.title = element_text(size = 22,
                                color = "brown"),
        panel.background = element_rect(fill = "linen"))

```

# Save the plot
```{r}
ggsave(here("Week_06","Output","Homework_for_Week_6b.png"),
       width = 8, height = 5) # in inches)
```

